GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis

### 2023-09-30 figs/GSE158422_split.Rmd
collect results

  # la1
  dm1 <- runlimma(mval_a,design_a,myann)
  dmagg1 <- agg(dm1,cores=CORES)
  m1 <- dmagg1$gme_res_df[,"mean",drop=FALSE]
  lares1 <- ttenrich(m=m1,genesets=gs_symbols,cores=CORES)
  lasig1 <- subset(lares1,fdr<0.01)

  # la2
  dm2 <- runlimma(mval_b,design_b,myann)
  dmagg2 <- agg(dm2,cores=CORES)
  m2 <- dmagg2$gme_res_df[,"mean",drop=FALSE]
  lares2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)
  lasig2 <- subset(lares2,fdr<0.01)

  lasig1_up <- rownames(subset(lasig1,t_median>0))
  lasig1_dn <- rownames(subset(lasig1,t_median<0))
  lasig2_up <- rownames(subset(lasig2,t_median>0))
  lasig2_dn <- rownames(subset(lasig2,t_median<0))

  ##v1 <- list("LA1 up"=lasig1_up, "LA1 dn"=lasig1_dn,
  ##  "LA2 up"=lasig2_up,"LA2 dn"=lasig2_dn)
  ## plot(euler(v1),quantities = TRUE)

  total <- length(unique(c(lasig1_up,lasig2_up,lasig1_dn,lasig2_dn)))
  common <- length(intersect(lasig1_up, lasig2_up)) + length(intersect(lasig1_dn, lasig2_dn))
  discordant <- length(intersect(lasig1_up, lasig2_dn)) + length(intersect(lasig1_dn, lasig2_up))
  uncommon = total - common - discordant
  result <- c("total"=total,"common"=common,"discordant"=discordant,"uncommon"=uncommon)
}

@@

@@

  ##v1 <- list("LA1 up"=lasig1_up, "LA1 dn"=lasig1_dn,
  ##  "LA2 up"=lasig2_up,"LA2 dn"=lasig2_dn)
  ## plot(euler(v1),quantities = TRUE)

  total <- length(unique(c(alsig1_up,alsig2_up,alsig1_dn,alsig2_dn)))
  common <- length(intersect(alsig1_up, alsig2_up)) + length(intersect(alsig1_dn, alsig2_dn))
  discordant <- length(intersect(alsig1_up, alsig2_dn)) + length(intersect(alsig1_dn, alsig2_up))
  uncommon = total - common - discordant
  result <- c("total"=total,"common"=common,"discordant"=discordant,"uncommon"=uncommon)
}

>>>>

  # la1
  dm1 <- runlimma(mval_a,design_a,myann)
  dmagg1 <- agg(dm1,cores=CORES)
  m1 <- dmagg1$gme_res_df[,"mean",drop=FALSE]
  lares1 <- ttenrich(m=m1,genesets=gs_symbols,cores=CORES)

  # la2
  dm2 <- runlimma(mval_b,design_b,myann)
  dmagg2 <- agg(dm2,cores=CORES)
  m2 <- dmagg2$gme_res_df[,"mean",drop=FALSE]
  lares2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)
}

@@

  list("alres1"=alres1,"alres2"=alres2)
}

alres

## Compare

```{r,compare}

lacompare <- function(lares){
  lares1 <- lares[[1]]
  lares2 <- lares[[2]]
  lasig1 <- subset(lares1,fdr<0.05)
  lasig2 <- subset(lares2,fdr<0.05)
  lasig1_up <- rownames(subset(lasig1,t_median>0))
  lasig1_dn <- rownames(subset(lasig1,t_median<0))
  lasig2_up <- rownames(subset(lasig2,t_median>0))
  lasig2_dn <- rownames(subset(lasig2,t_median<0))

  total <- length(unique(c(lasig1_up,lasig2_up,lasig1_dn,lasig2_dn)))
  common <- length(intersect(lasig1_up, lasig2_up)) + length(intersect(lasig1_dn, lasig2_dn))
  discordant <- length(intersect(lasig1_up, lasig2_dn)) + length(intersect(lasig1_dn, lasig2_up))
  uncommon = total - common - discordant

  lares <- as.data.frame(do.call(rbind,lares))
  lares$p_comm <-lares$common / lares$total
  lares$p_disc <-lares$discordant / lares$total
  lares$p_uncom <-lares$uncommon / lares$total
  lares
}

alcompare <-function(alres){
  alres1 <- alres[[1]]
  alres2 <- alres[[2]]
  alsig1 <- subset(alres1,fdr<0.05)
  alsig2 <- subset(alres2,fdr<0.05)

@@

  total <- length(unique(c(alsig1_up,alsig2_up,alsig1_dn,alsig2_dn)))
  common <- length(intersect(alsig1_up, alsig2_up)) + length(intersect(alsig1_dn, alsig2_dn))
  discordant <- length(intersect(alsig1_up, alsig2_dn)) + length(intersect(alsig1_dn, alsig2_up))
  uncommon = total - common - discordant
  result <- c("total"=total,"common"=common,"discordant"=discordant,"uncommon"=uncommon)

  alres <- as.data.frame(do.call(rbind,alres))
  alres$p_comm <-alres$common / alres$total
  alres$p_disc <-alres$discordant / alres$total
  alres$p_uncom <-alres$uncommon / alres$total
  alres
}
